Intergroup contact fosters\\more inclusive social identities

### 2019-11-06 manuscript/manuscript.tex
revision

% Frontmatter
\title{Intergroup contact fosters\\more inclusive social identities}
\date{July 30, 2019}

@@

\begin{abstract}
\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality). Participants judged each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded. Participants tended to exclude caste and religious minorities, replicating persistent social divides. Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes. Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' or ``not us''. Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged caste groups.\\[1ex]
\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action \\[1ex]
\end{abstract}

@@

@@

In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slideshow. Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us''). Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; $1 = \textit{very uncomfortable}$, $7 = \textit{very comfortable}$), and how they felt toward this person (feeling thermometer; $0 = \textit{cold}$, $100 = \textit{warm}$). Participants then completed the measures described below.

@@

We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}. We preceded these items with examples of positive and negative contact experiences. We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.47\leq\textit{rs}\leq.58$). Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.

@@

We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, for example, ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\alpha_\textit{Muslims} = .71$, $\alpha_\textit{Dalits} = .79$). Two items measured symbolic threat, e.g., ``[Muslims/ Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $r_\textit{Muslims} = .44$, $r_\textit{Dalits} = .48$).

@@

Five items measured policy support. Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''. Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $r_\textit{SC/ST} = .67$, $r_\textit{OBC} = .67$). Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''. Participants indicated to what extent they opposed or supported reservation for Muslim students.

@@

To answer these questions, we ran a series of multilevel logistic regression models with participants' target categorizations (1 = ``us'', 0 = ``not us'') as outcome variable. We estimated these models in RStan \cite{rstan_package} using Bayesian statistical methods. Bayesian inference involves choosing a likelihood function and prior distributions. The likelihood function links the observed data to one or more model parameters (e.g., regression coefficients) and states how likely the observed data are given different values of said model parameters. Prior distributions state how plausible different values of said model parameters are before considering the observed data. Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function. Our models assigned weakly informative prior distributions to all model parameters \cite{gelman_prior_2017}.\footnote{Our models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.}  Bayesian inference applies Bayes' theorem to update prior distributions in light of the observed data to produce posterior distributions. Other than $p$-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.\footnote{For a detailed introduction, consult \citeA{gelman_bayesian_2014}, \citeA{lambert_student_2018}, and	 \citeA{mcelreath_statistical_2016}.}

@@

\begin{table}
\caption{
Comparison of models estimating the probability of participants categorizing targets as ``us'' versus ``not us''. $\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\cite{vehtari_practical_2017}. $\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions. We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.%$w$ are stacking weights based on the models' expected log predictive densities \protect\cite{yao_using_2018}.
}
\centering
\figureversion{lining, tabular}
\small
\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - \\ 
1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 \\
2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 \\
3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 \\ \midrule
4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 \\
5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 \\
6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 \\
7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 \\
\bottomrule
\end{tabularx}
\label{tab:t2}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-4}
\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}). GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
\label{fig:f4}
\end{figure}

@@

@@

\begin{table}
\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations. As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$. $R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation \protect\fullcite{gelman_rsquared_2017}.}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - \\
1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 \\
2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 \\
3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 \\ \midrule
4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 \\
5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 \\
6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 \\
\bottomrule    
\end{tabularx}
\label{tab:t3}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-6}
\caption{
Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}). Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:f6}
\end{figure}

@@

We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations. To that end, we first estimated two multivariate regression models with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables. Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships. Model~1 estimated distinct means across participants' ingroups. Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $\textit{SE} = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$. This shows that participants' caste memberships shaped their perceived (dis )advantage and policy support ratings. Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences for the respective outcomes. Contradicting prevailing social inequalities, GM and OBC participants rated their own groups' lives as substantially harder than SC/ST members' lives. Policy support, in turn, strongly aligned with participants' caste interests. SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group. GM participants, for the most part, opposed reservation policies.

@@

Our research also examined support for social change. Contrary to past research, neither positive nor negative contact \cite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \cite{dixon_intergroup_2007} and disadvantaged \cite{dixon_beyond_2012} groups. Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}. Features of the participants' situation might explain this discrepancy. As university students, participants have personally experienced the impact of reservation policies. For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities. This experience might explain why these students strongly support reservation (at least for their own group). For GM students, reservation policies thwarted admission to state-funded universities. This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups \cite<see>{norton_whites_2011}.

>>>>

% Frontmatter
\title{Intergroup contact fosters\\more inclusive social identities}
\date{November 6, 2019}

@@

\begin{abstract}
\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality). Participants judged each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded. Participants tended to exclude caste and religious minorities, replicating persistent social divides. Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more positive relations between an advantaged, an intermediate, and a disadvantaged caste group. Negative contact was associated with less inclusive identities. Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, interminority relations, perceived discrimination, affirmative action \\[1ex]
\end{abstract}

@@

Most research on intergroup relations examines relations between an advantaged majority-group and a disadvantaged minority-group. Most social contexts, however, feature various groups facing various disadvantages. \citeA{craig_coalition_2012} argued that racial minorities may respond to the disadvantages they face by  derogating other racial minorities or by forming a coalition with them. The researchers showed that perceiving discrimination can, as far as it fosters a shared ingroup identity with other disadvantaged groups, improve interminority relations. \citeA{vollhardt_inclusive_2016} observed that South Indians from disadvantaged caste and religious groups were more likely to express support for another disadvantaged group when they recognized similarities between their own and other groups' experiences of discrimination. \citeA{dixon_contact_2017} found that Indian Muslims who reported having more contact with other disadvantaged groups were also more likely to recognize shared grievances and to express support for collective action benefiting all disadvantaged groups. Our research adds to this literature by examining intergroup relations between two disadvantaged groups, one of which occupies an intermediate position in the social hierarchy. We examine whether, by fostering shared ingroup identities, contact between disadvantaged groups can foster more positive intergroup relations, shared perceptions of relative disadvantage, and mutual support for affirmative action.

@@

In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slide show. Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us''). Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; $1 = \textit{very uncomfortable}$, $7 = \textit{very comfortable}$), and how they felt toward this person (feeling thermometer; $0 = \textit{cold}$, $100 = \textit{warm}$). Participants then completed the measures described below.

@@

We report two reliability indices for our measures, the Spearman-Brown statistic ($\rho$) for two-item measures \cite{eisinga_reliability_2013} and McDonald's omega ($\omega$) for multi-item measures \cite{dunn_alpha_2014}.

We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}. We preceded these items with examples of positive and negative contact experiences. We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.65 < \rho < .71$). Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.

@@

We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, for example, ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\omega_\textit{Muslims} = .71$, $\omega_\textit{Dalits} = .79$). Two items measured symbolic threat, e.g., ``[Muslims/ Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\rho_\textit{Muslims} = .61$, $\rho_\textit{Dalits} = .65$).

@@

Five items measured policy support. Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''. Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $\rho_\textit{SC/ST} = .80$, $\rho_\textit{OBC} = .80$). Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''. Participants indicated to what extent they opposed or supported reservation for Muslim students.

@@

To answer these questions, we ran a series of multilevel logistic regression models with participants' target categorizations (1 = ``us'', 0 = ``not us'') as outcome variable. We estimated these models in RStan \cite{rstan_package} using Bayesian statistical methods. Bayesian inference involves choosing a likelihood function and prior distributions. The likelihood function links the observed data to one or more model parameters (e.g., regression coefficients) and states how likely the observed data are given different values of said model parameters. Prior distributions state how plausible different values of said model parameters are before considering the observed data. Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function. Our models assigned conservative, weakly informative prior distributions to all model parameters \cite{gelman_prior_2017}.\footnote{Our models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.}  Bayesian inference applies Bayes' theorem to update prior distributions in light of the observed data to produce posterior distributions. Other than $p$-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.\footnote{For a detailed introduction, consult \citeA{gelman_bayesian_2014}, \citeA{lambert_student_2018}, and	 \citeA{mcelreath_statistical_2016}.}

\begin{table}
\caption{
Comparison of models estimating the probability of participants categorizing targets as ``us'' versus ``not us''. $\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\cite{vehtari_practical_2017}. $\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions. We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.%$w$ are stacking weights based on the models' expected log predictive densities \protect\cite{yao_using_2018}.
}
\centering
\figureversion{lining, tabular}
\small
\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - \\ 
1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 \\
2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 \\
3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 \\ \midrule
4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 \\
5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 \\
6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 \\
7 & vs 2 & SDO-D \& SDO-E & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 \\
\bottomrule
\end{tabularx}
\label{tab:t2}
\end{table}

@@

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=1]{../figures/figure-4}
\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}). GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
\label{fig:f4}
\end{figure}

@@

\begin{table}[t!]
\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations. As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$. $R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation \protect\fullcite{gelman_rsquared_2017}.}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - \\
1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 \\
2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 \\
3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 \\ \midrule
4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 \\
5 & vs 4 & ... (Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 \\
6 & vs 5 & ... (Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 \\
\bottomrule    
\end{tabularx}
\label{tab:t3}
\end{table}

@@

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=1]{../figures/figure-6}
\caption{
Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}). Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:f6}
\end{figure}

@@

We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations. To that end, we first estimated two multivariate regression models with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables. Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships. Model~1 estimated distinct means across participants' ingroups. Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $\textit{SE} = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$. This shows that participants' caste memberships shaped their perceived (dis-)advantage and policy support ratings. Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences for the respective outcomes. Contradicting prevailing social inequalities, GM and OBC participants rated their own groups' lives as substantially harder than SC/ST members' lives. Policy support, in turn, strongly aligned with participants' caste interests. SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group. GM participants, for the most part, opposed reservation policies.

@@

Our research also examined support for social change. Contrary to past research, neither positive nor negative contact \cite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \cite{dixon_intergroup_2007, selvanathan_whites_2018} and disadvantaged \cite{dixon_beyond_2012} groups. Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}. Features of the participants' situation might explain this discrepancy. As university students, participants have personally experienced the impact of reservation policies. For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities. This experience might explain why these students strongly support reservation (at least for their own group). For GM students, reservation policies thwarted admission to state-funded universities. This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups \cite<see>{norton_whites_2011}.
